### 2016-07-26 doc/manual/version3/inputParameters.tex
Updated manual with new parameters related to Phi1 calculations

@@

\param{includePhi1}
{Boolean}
{\false}
{Whenever \parlink{RHSMode} == 1.}
{If false, no terms involving $\Phi_1 = \Phi-\left<\Phi\right>$ are included in the kinetic equation,
and the quasineutrality equation is not solved.  If true, then terms involving $\Phi_1$ are included
in the kinetic equation, and the quasineutrality equation is solved at each point on the flux surface.
In this latter case, many more quantities are computed and saved in the output file, such as radial fluxes
associated with the radial $\vect{E}\times\vect{B}$ drift.}

@@

\param{includeRadialExBDrive}
{Boolean}
{\false}
{Whenever \parlink{RHSMode} == 1.}
{If true, the radial $\vect{E}\times\vect{B}$ term $(\vect{v}_{E} \cdot\nabla\psi)f_{Ms} [(1/n_s)(dn_s/d\psi) + (x_s^2-3/2)(1/T_s)(dT_s/d\psi)]$
will be included in the kinetic equation. This is one of the terms considered in Ref \cite{Regana2013} which
should be unimportant for the main ions but which may be important for impurities.
Use of this option requires \parlink{includePhi1}=\true, since the radial $\vect{E}\times\vect{B}$ drift
arises due to $\Phi_1$.
}

@@

\param{nonlinear}
{Boolean}
{\false}
{Whenever \parlink{RHSMode} == 1.}
{If true, the term
$-(Z_s e/m) (\nabla_{||} \Phi_1) (\partial f_{s1}/\partial v_{||})_\mu$ will be included
in the kinetic equation.  This is one of the terms considered in Ref \cite{Regana2013} which
should be unimportant for the main ions but which may be important for impurities.
This term is nonlinear in the unknowns $f_{s1}$ and $\Phi_1$.
Newton's method will be used to solve the nonlinear system, meaning that the usual linear solve in \sfincs~must
be iterated several times.
Running with {\ttfamily nonlinear}=\true requires \parlink{includePhi1}=\true
}

>>>>

\param{withAdiabatic}
{Boolean}
{\false}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true}
{If this parameter is \true, an adiabatic species is added into the quasineutrality equation (but has no other effect).}

\param{adiabaticZ}
{real}
{-1.0}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true and \parlink{withAdiabatic} == \true}
{Charge of adiabatic species, in units of the proton charge $e$.}

\param{adiabaticMHat}
{real}
{5.44617e-4}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true and \parlink{withAdiabatic} == \true}
{Mass of adiabatic species, in units of the reference mass $\bar{m}$.}

\param{adiabaticNHat}
{real}
{1.0}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true and \parlink{withAdiabatic} == \true}
{Density of adiabatic species, in units of the reference density $\bar{n}$.}

\param{adiabaticTHat}
{real}
{1.0}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true and \parlink{withAdiabatic} == \true}
{Temperature of adiabatic species, in units of the reference temperature $\bar{T}$.}

@@

\param{includePhi1}
{Boolean}
{\false}
{Whenever \parlink{RHSMode} == 1.}
{If false, no terms involving $\Phi_1 = \Phi-\left<\Phi\right>$ are included in the kinetic equation,
and the quasineutrality equation is not solved.  If true, then terms involving $\Phi_1$ are included
in the kinetic equation if \parlink{includePhi1inKineticEquation} = \true, and the quasineutrality equation is solved at each point on the flux surface (make sure that your input densities fulfill quasineutrality, see \parlink{quasineutralityOption}). 
In this latter case, many more quantities are computed and saved in the output file, such as radial fluxes
associated with the radial $\vect{E}\times\vect{B}$ drift.\newline
%%Text added by AM 2016-07
If true, the system becomes nonlinear in the unknowns $f_{s1}$ and $\Phi_1$. 
Newton's method will be used to solve the nonlinear system, meaning that the usual linear solve in \sfincs~must be iterated several times.
}

@@

\param{includePhi1inKineticEquation}
{Boolean}
{\true}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true}
{If true, the terms containing $\Phi_1$ will be included in the kinetic equation. 
If false, and \parlink{includePhi1} = \true, then $\Phi_1$ is only included in the quasineutrality equation. 
}

@@

\param{quasineutralityOption}
{integer}
{1}
{Whenever \parlink{RHSMode} == 1 and \parlink{includePhi1} == \true}
{This variable controls which quasineutrality equation is used, and must be set to either 1 or 2. Make sure that your input densities fulfill quasineutrality (also accounting for the adiabatic species if \parlink{withAdiabatic}=\true).\\

{\ttfamily quasineutralityOption} = 1: Full quasineutrality equation. All species (kinetic and adiabatic if applicable) are included in the quasineutrality equation.\\

{\ttfamily quasineutralityOption} = 2: {\ttfamily EUTERPE} quasineutrality. \sfincs~must be run with an adiabatic species, \parlink{withAdiabatic}=\true, and only the adiabatic species and the first kinetic species are included in the quasineutrality equation (their input densities must fulfill quasineutrality). This is the quasineutrality considered in Ref \cite{Regana2013}.
}

%%The includeRadialExBDrive parameter has been removed by AM 2016-07
%\myhrule
%
%\param{includeRadialExBDrive}
%{Boolean}
%{\false}
%{Whenever \parlink{RHSMode} == 1.}
%{If true, the radial $\vect{E}\times\vect{B}$ term $(\vect{v}_{E} \cdot\nabla\psi)f_{Ms} [(1/n_s)(dn_s/d\psi) + (x_s^2-3/2)(1/T_s)(dT_s/d\psi)]$
%will be included in the kinetic equation. This is one of the terms considered in Ref \cite{Regana2013} which
%should be unimportant for the main ions but which may be important for impurities.
%Use of this option requires \parlink{includePhi1}=\true, since the radial $\vect{E}\times\vect{B}$ drift
%arises due to $\Phi_1$.
%}

%%The nonlinear parameter has been removed by AM 2016-07
%\myhrule
%
%\param{nonlinear}
%{Boolean}
%{\false}
%{Whenever \parlink{RHSMode} == 1.}
%{If true, the term
%$-(Z_s e/m) (\nabla_{||} \Phi_1) (\partial f_{s1}/\partial v_{||})_\mu$ will be included
%in the kinetic equation.  This is one of the terms considered in Ref \cite{Regana2013} which
%should be unimportant for the main ions but which may be important for impurities.
%This term is nonlinear in the unknowns $f_{s1}$ and $\Phi_1$.
%Newton's method will be used to solve the nonlinear system, meaning that the usual linear solve in \sfincs~must
%be iterated several times.
%Running with {\ttfamily nonlinear}=\true requires \parlink{includePhi1}=\true
%}
